Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-10 WSSSPE3/report/wg_appendix_funding_spec_expert.tex

In this respect, information gatheirng via a survey subsequent analysis could be very useful.
We would need to assemble a list of targetted individuals (what position and rank is
likely to know and care enough to respond?) Perhaps the Science Gateway Insitute has already acquire
information that could be helpful to advance this issue, and/or craft the proper survey and target
individuals.

@@

In the longer term, funding organizations, especially non-governmental organizations
with the capability to effect innovation through seed funding, could provide
support to nucleate the creation of research software groups. As noted above, Sloan has already
initiated one such program, and collaboration with Slaon or at least study of their methods and 
success or failure could be extremely useful in approaching Universities and other insitutions 
in funding this development track. It seems clear that if the value proposition can be made to
University adminstrators, this track could flourish with buy-in at the adminstrative level.

>>>>

In this respect, information gathering via a survey subsequent analysis could be very useful.
We would need to assemble a list of targeted individuals (what position and rank is
likely to know and care enough to respond?) Perhaps the Science Gateway Institute has already acquire
information that could be helpful to advance this issue, and/or craft the proper survey and target
individuals.

@@

In the longer term, funding organizations, especially non-governmental organizations
with the capability to effect innovation through seed funding, could provide
support to nucleate the creation of research software groups. As noted above, Sloan has already
initiated one such program, and collaboration with Sloan or at least study of their methods and 
success or failure could be extremely useful in approaching Universities and other institutions 
in funding this development track. It seems clear that if the value proposition can be made to
University administrators, this track could flourish with buy-in at the administrative level.
